---
title: "REF_MRP_CONTROLLER"
author: "Shantanu Mendhekar"
date: "Last Update: `r format(Sys.time(), '%B %d, %Y, %X')`"
---

<script src="libs/locationhash.js"></script>

# Summary {.tabset .tabset-fade .tabset-pills}

## Contacts

Table Owner - [Craig Piche](mailto:craig.piche@ericsson.com?subject=QUERY: REF_MRP_CONTROLLER)  
Table Developer - [Sharon Atkinson](mailto:sharon.xx.atkinson@ericsson.com?subject=QUERY: REF_MRP_CONTROLLER)  
Table Users - Supply Americas 

## Git

```{r, eval = FALSE}

```

# Info

The REF_MRP_CONTROLLER has information about the current person responsible for a Commodity in the different areas of the Supply Chain. The areas being:

- [Commodity Planners](https://ericsson.sharepoint.com/sites/RNAM_Supply/IntegratedPlanning/CommodityPlanning/Pages/home.aspx) - Responsible for identifying needs and issues, expedite the activities to maintain optimum material levels, facilitate commodity transfer, and improve stock management processes.
  
- [Material Managers](https://ericsson.sharepoint.com/sites/RNAM_Supply/IntegratedPlanning/Procurement/Pages/home.aspx) - Responsible for procuring items are aligning with contractual terms and conditions, benchmarking with standard lead-times, and ensure delivery precision key performance indicators support successful end customer deployment satisfaction.

- Commodity Buyer

- [Sourcing Prime](https://internal.ericsson.com/book/23106/north-america-strategic-sourcing?unit=31552270) - Responsible for developing the sources of supply for Products and Services for stakeholders across the region. They provide an appropriate balance of cost, quality, and service from the suppliers.

- PPM Manager

# To Update

<form method="post" action="mailto:email.com?subject=" + firstname + "&message=lastname">
  First name:<br>
  <input type="text" name="firstname" id="test1" value1="">
  <br>
  Last name:<br>
  <input type="text" name="lastname" value2="">
  <br>
  <input type="submit" value="Submit">
</form>

# Test2

<form action="/action_page.php" onsubmit="myFunction()">
  Enter name: <input type="text" name="name" id="uniqueID">
  <input type="submit" value="Submit">
</form>

<script>
var nameValue = document.getElementById("uniqueID").value;

function myFunction() {
    alert("The form was submitted" + nameValue);
}
</script>

# Test 3

<form name="input" action="handle_email.php" method="post">
  <input type="text" name="email" id="email" />
  <input type="submit" value="Submit" />
</form> 

<script>
   $("form").submit(function() {
     var emailFromOtherTextBox = $("#email_textbox").val();
     $("#email").val(emailFromOtherTextBox ); 
     return true;
  });
</script>

# Table

```{r, message=FALSE, warning=FALSE }
library(RODBC)
library(DT)

# Connect to SQL Server
connection <- odbcConnect("REPORTINGDB")

Query = "
SELECT *
FROM REF_MRP_CONTROLLER
"

# Extract Data
Data <- sqlQuery(connection, Query)

# Close SQL Server Connection
odbcCloseAll()

# Create Datatable
datatable(Data
  ,extensions = c('Buttons', 'Scroller')
  ,class = 'cell-border stripe'
  ,style = "default"
  ,options = list(order = list(list(1, 'asc'))
    ,pageLength = 20
    # ,autoWidth = TRUE
    ,deferRender = TRUE
    ,scrollY = 1000
    ,scroller = TRUE
    ,scrollX = TRUE
    ,dom = 'Bfrtip', buttons = c('copy','excel'))
)
```
